\section{Discussion\label{discussion}}
Our results indicate that the privacy properties of Kadcast are not optimal. \\
We did not do a thorough analysis as to why this is the case, as this would
be out of scope for this report. \\
If one were to further investigate the cause of this result, there are
many interesting open questions.
For example, it would be interesting to analyze if the privacy properties change
if the broadcast is sent to the buckets in reverse order. Kadcast
first sends the broadcast to the bucket which is furthest away, as this also
means it has the largest routing subtree. Afterwards broadcast messages
are sent to other buckets in descending order. This is done to achieve
fair spreading characteristics [], although it is not clear how this
relates to the anonymity of the network. Our assumption is, that sending
the message to the largest subtree first reduces the probability of
directly hitting an adversarial node. \\
In our analysis we also assumed the adversary does not take the network topology into account.
It would be interesting to drop this assumption and do further research on what kind of
information a less ``naive'' attacker could exploit. \\
For example, one could explore if it would be possible for an attacker to infer additional information
about the bucket layout of sending nodes, and utilize this information to create a more sophisticated estimator. \\
If the attacker could somehow identify some nodes as being far away or close by (according to the XOR distance),
they could e.g. weight their obvervations by proximity, as a close node has a higher chance to have a direct link
to a node. \\
To really understand the boundaries of an attack, it would further be of interest to
investigate the symmetry properties[] of the message spreading. \\
In general, it would be of great benefit if our results were reinforced either
by a more realistic simulation that closer resembles real world
scenarios, e.g. by including failures, or
by a formal model that gives a better understanding of the theoretical
limits of an attack.
